Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-14 WSSSPE2_report/WSSSPE2_review.tex
Section 4: touch up.

%\item John W Peterson: Continuous Integration for Concurrent MOOSE Framework and
%Application Development on GitHub

>>>>

\item \textbf{John Peterson: Continuous Integration for Concurrent MOOSE Framework and
Application Development on GitHub}

%Affiliation: Idaho National Laboratory

Peterson from the the Idaho National Laboratory reported that in March 2014, the MOOSE framework was released under an open
source license on GitHub, significantly expanding and diversifying the pool of
current active and potential future contributors on the project. The MOOSE team
employs an extensive continuous integration test suite to ensure that both the
framework and the applications based on the framework are verified before any
code changes are accepted into the repository. They use a combination of built-in
git features such as branching and submodules, GitHub API integration
capabilities, and in-house developed testing software to perform this
verification and update the dependent applications in a relatively seamless
manner for users.
